---
output:
  md_document:
    variant: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# RCapstone

The goal of RCapstone is to clean, timeline and map NOAA Significant Earthquake data. The package was built for the Capstone project of the Coursera Mastering Software Development in R specialization.

## Installation:

To install the package first install and load the devtools package. Then run:

```{r}
devtools::install_github("JulianTWolf/RCapstone")
library(RCapstone)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(dplyr)
library(ggplot2)
library(RCapstone)
data_raw <<- readr::read_delim("/Users/julian/Documents/07 Sonstiges/R-Projekte/RCapstone/signif.txt.tsv", col_names=T, delim = "\t")
eq_location_clean(data_raw)
eq_clean_data(data_loc_clean)

data_clean %>% dplyr::filter(COUNTRY %in% c('USA', 'UK')) %>% dplyr::filter(DATE > '2000-01-01') %>% ggplot(aes(x = DATE, y = COUNTRY, color = TOTAL_DEATHS, size = EQ_PRIMARY)) + geom_timeline()

data_clean %>% dplyr::filter(COUNTRY == "MEXICO" & lubridate::year(DATE) >= 2000) %>%
  dplyr::mutate(popup_text = eq_create_label(.)) %>%
  eq_map(annot_col = "popup_text")
```
